Analysis of Odd one out experiment

### 2019-06-27 reports/DRM_exp/analysis_DRM_exp1.Rmd
change to svg instead eps
code reorganisation

@@

@@

p <- df %>%
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = .5) +
  ylab("Perc. correct") +
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Type")

p
ggsave(file.path(plots_dir, "Fig_chp4_results_accuracy.eps"), p, width = 6, height = 6)

@@

```{r}
p <- df %>% 
  filter(rt_key < 5) %>% 
  ggplot(aes(x = rt_key)) + 
  theme(aspect.ratio = 1) +
  geom_histogram(binwidth = 0.2) + 
  xlab("RT [s]")
p
ggsave(file.path(plots_dir, "Fig_chp4_results_rt_hist.eps"), p, width = 6, height = 6)

p <- df_rt %>% 
  group_by(subject_id, type) %>% 
  summarize(rt = mean(rt_key)) %>% 
  ggplot(aes(x = type, y = rt)) + 
  theme(aspect.ratio = 1) +
  ylab("RT [s]") +
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Type")
p
ggsave(file.path(plots_dir, "Fig_chp4_results_rt.eps"), p, width = 6, height = 6)
```

@@

ggsave(file.path(plots_dir, "Fig_chp4_results_perhalves.eps"), p, width = 6, height = 6)
```

@@

p1 <- df_oldclose %>% ggplot(aes(x = FAs, y = Hs, group = as.factor(subject_id))) + 
  geom_path(alpha = I(0.2)) + 
  xlim(0,1) + 
  ylim(0,1) + 
  geom_segment(x = 0, y = 0, xend = 1,yend = 1) +
  theme(aspect.ratio = 1) +
  geom_path(data = df_oldclose_agg, group = 1, size = 1.5, col = "red") + 
  ggtitle("Target-close distractor discrimination")

p2 <- df_oldfar %>% ggplot(aes(x = FAs, y = Hs, group = as.factor(subject_id))) + 
  geom_path(alpha = I(0.2)) + 
  xlim(0,1) + 
  ylim(0,1) + 
  geom_segment(x = 0, y = 0, xend = 1,yend = 1) +
  theme(aspect.ratio = 1) +
  geom_path(data = df_oldfar_agg, group = 1, size = 1.5, col = "red") + 
  ggtitle("Target-far distractor discrimination")

>>>>

# Load libraries

@@

Data were preprocesseb by scripts

@@

p <- df %>%
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = .5) +
  ylab("Perc. correct") +
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Type") +
  theme(text = element_text(size = 24))

p
ggsave(file.path(plots_dir, "Fig_chp4_results_accuracy.svg"), p, width = 6, height = 6)

@@

```{r}
p <- df %>% 
  filter(rt_key < 5) %>% 
  ggplot(aes(x = rt_key)) + 
  theme(aspect.ratio = 1) +
  geom_histogram(binwidth = 0.2) + 
  xlab("RT [s]") + 
  theme(text = element_text(size = 24))
p
ggsave(file.path(plots_dir, "Fig_chp4_results_rt_hist.eps"), p, width = 6, height = 6)

p <- df_rt %>% 
  group_by(subject_id, type) %>% 
  summarize(rt = mean(rt_key)) %>% 
  ggplot(aes(x = type, y = rt)) + 
  theme(aspect.ratio = 1) +
  ylab("RT [s]") +
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Type") +
  theme(text = element_text(size = 24))
p
ggsave(file.path(plots_dir, "Fig_chp4_results_rt.svg"), p, width = 6, height = 6)
```

@@

ggsave(file.path(plots_dir, "Fig_chp4_results_perhalves.svg"), p, width = 6, height = 6)
```

@@

p1 <- df_oldclose %>% ggplot(aes(x = FAs, y = Hs, group = as.factor(subject_id))) + 
  geom_path(alpha = I(0.2)) + 
  xlim(0,1) + 
  ylim(0,1) + 
  geom_segment(x = 0, y = 0, xend = 1,yend = 1) +
  theme(aspect.ratio = 1) +
  geom_path(data = df_oldclose_agg, group = 1, size = 1.5, col = "red") + 
  ggtitle("Target - Close distractor") +
  theme(text = element_text(size = 24))

p2 <- df_oldfar %>% ggplot(aes(x = FAs, y = Hs, group = as.factor(subject_id))) + 
  geom_path(alpha = I(0.2)) + 
  xlim(0,1) + 
  ylim(0,1) + 
  geom_segment(x = 0, y = 0, xend = 1,yend = 1) +
  theme(aspect.ratio = 1) +
  geom_path(data = df_oldfar_agg, group = 1, size = 1.5, col = "red") + 
  ggtitle("Target - Far distractor") +
  theme(text = element_text(size = 24))

### 2019-06-27 reports/odd_one_out/analysis_oddoneout.Rmd
code reorganisation

  #scale_x_continuous("Kvintil", breaks = c(2,3,4), labels = c("2","3","4")) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Quintile") + 
  facet_wrap(~subject_id, ncol = 4)

p
ggsave(file.path(plots_dir, "Fig_chp3_results_participants.eps"), p, width = 6, height = 6)

@@

predframe$correct <- predict(glm2,newdata=predframe,type="response",re.form=NA)
p <- p0 + geom_point(data=predframe,colour="red")+
  geom_line(data=predframe,colour="red",aes(group=1)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  xlab("Distance ratio") + 
  ylab("Perc. correct")

@@

    theme(aspect.ratio = 1) + 
    xlab("MDS 1") + ylab("MDS 2") + 
    ggtitle(sprintf("Category: %s", cat_name)) +
    scale_color_manual(values = c("green","blue","red"))
  p
}
bottom_one <- order_category %>% filter(rank == 1)
top_one <- order_category %>% filter(rank == 64)
fc7_names <- colnames(fc7)

>>>>

  #scale_x_continuous("Kvintil", breaks = c(2,3,4), labels = c("2","3","4")) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Quintile") + 
  theme(text = element_text(size = 16)) +
  facet_wrap(~subject_id, ncol = 4)

p
ggsave(file.path(plots_dir, "Fig_chp3_results_participants.svg"), p, width = 6, height = 6)

@@

predframe$correct <- predict(glm2,newdata=predframe,type="response",re.form=NA)
p <- p0 + geom_point(data=predframe,colour="red")+
  geom_line(data=predframe,colour="red",aes(group=1)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  xlab("Distance ratio") + 
  ylab("Perc. correct") +
  theme(text = element_text(size = 24))

@@

    theme(aspect.ratio = 1) + 
    xlab("MDS 1") + ylab("MDS 2") + 
    ggtitle(sprintf("Category: %s", cat_name)) +
    scale_color_manual(values = c("green","blue","red")) +
    theme(text = element_text(size = 20)) 
  p
}
bottom_one <- order_category %>% filter(rank == 1)
top_one <- order_category %>% filter(rank == 64)
fc7_names <- colnames(fc7)
